WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-04-25 summary/sec_1-conclusions.tex
Replace noun acronym with full word
Updated Summary - Chapter5

To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}. Even though there are many weather data integration systems, most of them are proprietary or closed source. This means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. %\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
\hl{Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems. Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.}

\dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
\gkc{UPDATED}

We proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}. \acrshort{wdias} focuses on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data. And compatible with current cloud computing technologies and architecture patterns.

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to Actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture.
\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}. Each microservice of \acrshort{wdias} is mapped to a pod in the \acrshort{k8s}. Also, each microservice follows the concept of Smart endpoints dumb pipes and does specific operations that are related to the data format that responsible for handling.

Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of database structure to provide higher performance while storing the weather data optimum. The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data. And each database adapter uses the concept of database per service which allows each microservice service to scale without interference from other microservices.
And it uses microservice sagas pattern for asynchronous data handling for requests with higher size. According to the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system. This capability enables to integrate weather data preprocessing flows as extension modules.
The extension API provides easy access to create and modify the extension triggers on the fly without stopping the system or any downtime to change the configurations.
The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo-based queries.

Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}. Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform the same while keeping the latency constant without any significant change. During the performance test plans, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Which exhibits the scalability of the system.
With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto-scaling configurations. 
The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.

>>>>

To enhance the accuracy of the weather prediction, we need to provide reliable and timely weather data for NWMs. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized. Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we can not get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.

During our research, we proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}. \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data. Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to Actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.

Based on the microservice architecture patterns and the nature of the weather metadata, we came up with the idea of database structure for the \acrshort{wdias} to provide higher performance while storing the weather data optimum. The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data. Also, each database has an adapter, and each adapter uses the concept of database per service, which allows each microservice service to scale without getting interference from other microservices.
Moreover, it uses the microservice sagas pattern for asynchronous data handling for requests with a larger size. As discussed in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system. This capability enables us to integrate weather data preprocessing flows as extension modules.
We designed an extension API to easily access to create and modify the extension triggers at runtime without stopping the system or any downtime for the system reconfiguration. The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting Geo-based queries.

Further, we performed load tests using the JMeter tool’s distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. The system is setup on the Amazon Elastic Kubernetes Service (Amazon EKS) as per the system setup configurations of \cref{subse:test_sys_config}. Based on the observations, we were able to perform 300 \acrshort{rps} of peak load, and the system handled the workload successfully with minimizing the error rate to zero. Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant without any significant change. Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Thus, we can conclude that the system is further scalable.
With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations. The results of \acrshort{wdias} shows that the system can run on a cluster from 1 CPU node to nodes with a few hundred CPUs.

### 2020-04-25 summary/sec_2-research_limitations.tex
Updated Summary - Chapter5

\section{Research Limitations}
\label{se:research_limitations}
\gkc{Previously you asked to rename this section sir. Why can't it have the title of \emph{Future Work}. There are some of the requirements that can be done for the system, in order to gain more of it. Which part is misleading?}

This section discussed the lacking features in the \acrshort{wdias} and some of the improvements that can add to improve the performance and usability of the system.

\emph{Lack of data preprocessing modules}:
The extension module enables the plugin system to integrate prepossessing modules that can use for process the data which are inserted to the system or based on regular intervals. Also, \acrshort{wdias} provides a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open-source system, it expects more modules to be created by the community. When compared to other systems like \acrshort{fews}, the current system only have few extension for the testing purpose. This is one of the major areas that need to be improved.

\emph{Supporting Irregular Grids}:
At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation which can follow the same microservice architecture. The scope of the \acrshort{wdias} does not belong to such level of implementation and the scope was reduced by removing such components from the system.

\emph{Grid data performance}:
As mentioned in the \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low-level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

\emph{Define infrastructure as code}:
Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}. And defining each pod resource limitations at the helm chart level. But the infrastructure that needs to deploy the \acrshort{wdias} can define as code such as using tools like Terraform which is independent of the Cloud Computing provider. Using such a tool, users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle.

\emph{Improve test cases}:
As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses the \emph{Time Stepping Feedback} loop with Concurrent Threads which is the best approach support by  JMeter at the moment. But using that it is not possible to get the desired \acrshort{rps} for each test case within the test plan.
Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning. Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases. Still, there may be some improvement that can be done.

\emph{Tune \acrshort{wdias} database structure performance}:
As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB. With the  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple  InfluxDB instances. The adapter-scalar or adapter-vector can improve to plug multiple instances of  InfluxDB instances by changing the configurations. As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of  InfluxDB instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast, etc.

\emph{Alerting extension modules}:
At the moment, extensions only support \emph{OnChange} and \emph{OnTime} events. But it will be good to have event trigger support based on reconfigured alert level.

\emph{Publisher Subscriber extension modules}:
The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.

\dbc{Need a new section for Conclusions.}
\gkc{It did not make sense for me to adding another section as Conclusion. We already add a \cref{se:summary_conclusion} above. Do we need to rearrange the content of this Chapter? No point of adding another section with repeating the same content. May be I didn't understand your suggestion here.}
\gkc{Do we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}

>>>>

\section{Research Limitations}
\label{se:research_limitations}

During this Section, we discussed the lacking features of the \acrshort{wdias} and the set of improvements that we can add to improve the performance and usability of the system.

\emph{Lack of data preprocessing modules}:
We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the system. Then, users can use these modules for process the data which are inserted into the system in real time or process later based on regular intervals. Also, we provide a more generic open interface approach to create more preprocessing modules and trigger them via the extension API. Since \acrshort{wdias} is an open-source system, we are expecting that the community will create more modules, and provide them as contributions for future users. When compared to other systems like \acrshort{fews}, the current system only has few extensions for the testing purpose. Thus, we can consider that as one of the major areas that need to be improved.

\emph{Supporting Irregular Grids}:
At the moment, \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture. We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.

\emph{Grid data performance}:
As mentioned in \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. However, it has some performance issues and memory leak issues as well. Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service. As an example, we can use a low-level language such as C or FORTRAN to implement the adapter-grid, which will affect performance improvements and lesser issues. There is some future work that can focus on improving the performance of storing grid data.

\emph{Define infrastructure as code}:
Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud. However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider. Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.

\emph{Improvements to test cases}:
As described in detail with \cref{subse:closed_vs_open_workload}, the \acrshort{wdias} test plans use the time-stepping feedback loop with concurrent threads, which is the best approach support by JMeter at the moment. However, using the above approach, we can not get the desired \acrshort{rps} for each test case within the test plan.
Because of the above issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning. Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case, rather than running the required test cases. Thus, the test plans need to be further improved with running more test cases with the desired \acrshort{rps}.

\emph{Tune \acrshort{wdias} database structure performance}:
As further described in \cref{se:discussion}, we can increase the performance of adapter microservices by using InfluxDB commercial cluster support for high availability or horizontal scaling of InfluxDB. With the InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector to support more server hits per second. Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries keyspace into multiple InfluxDB instances. As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of InfluxDB instances such as External Historical, External Forecast, Simulated Historical, and Simulated Forecast.
\emph{Alerting extension modules}: At the moment, extensions only support OnChange and OnTime events. However, it will be useful to have event trigger support based on the configured alert level or threshold level. 
\emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.
